### 2020-06-11 writeup/related.tex
impact

In this work, we provide a theoretical study to help understand when multi-task learning performs well.
We approach this question by studying the bias-variance tradeoff of multi-task learning.
We provide new technical tools to bound the bias and variance.
We relate the bounds to three properties of task data.
%Overall, our theoretical study provides a framework to help understand multi-task learning performance.
We further provide guidance for detecting and mitigating negative transfer on image and text classification tasks.

Our theoretical framework has the potential to impact many other neighboring areas in the ML community.
Multi-task learning connects to a wide range of areas \cite{V20}.
To name a few, transfer learning, meta learning, multimodal learning, semi-supervised learning, and representation learning are all closely related areas to multi-task learning.
Any learning scenario such as reinforcement learning \cite{YKGLHF20} that combines multiple datasets to supervise a model is using multi-task learning.
While the theoretical results that we have provided are not directly applicable to these different settings, we believe that the tools we have developed and the framework we have provided can inspire followup works in different settings.
For one specific example, we have developed new concentration bounds that may apply to many settings such as soft parameter sharing \cite{R17} , kernel methods \cite{EMP05}, and convex formulation of multi-task learning \cite{ZY14}.
For another example, our results also allow extensions to transfer learning and domain adaptation \cite{K18}.
The insights we have developed on positive and negative transfer can potentially find applications in multimodal learning, where the data sources are usually heterogeneous.
Our fine-gained study on sample sizes have the potential to provide new insight in meta learning, where scarse labeled samples presents a significant challenge.

Our algorithmic consequences of our theory have the potential to impact downstream applications of multi-task learning.
For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult to acquire large amounts of labeled data.
For such settings, training multi-task models can be very challenging.
Our insight on using single-task learning results to help understand multi-task learning can be valuable for helping practitioners understand their results.

>>>>

In this work, we provide a theoretical framework to help understand when multi-task learning performs well.
We approach this question by studying the bias-variance tradeoff of multi-task learning.
We provide new technical tools to bound the bias and variance.
%We relate the bounds to three properties of task data.
%Overall, our theoretical study provides a framework to help understand multi-task learning performance.
%We further provide guidance for detecting and mitigating negative transfer on image and text classification tasks.

Our theoretical framework has the potential to impact many other neighboring areas in the ML community.
(i) Our concentration bounds are applicable to different settings such as soft parameter sharing \cite{R17} , kernel methods \cite{EMP05}, and convex formulation of multi-task learning \cite{ZY14}.
(ii) Our analysis of the bias-variance tradeoff can be extended to transfer learning and domain adaptation \cite{K18}.
(iii) Our insights on positive and negative transfer can potentially find applications in multimodal learning, where the data sources are usually heterogeneous.
(iv) Our fine-gained study on sample sizes have the potential to provide new insight in meta learning, where scarse labeled samples presents a significant challenge.
Finally, since multi-task learning connects to a wide range of areas \cite{V20} such as semi-supervised learning, representation learning, and reinforcement learning \cite{YKGLHF20}.%
We believe that the tools we have developed and the framework we have provided can inspire followup works in these different areas.

Our proposed algorithmic consequences also have the potential to help both researchers and practitioners to better develop their multi-task learning applications.
For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult and expensive to acquire large amounts of labeled data.
For such settings, our proposed training scheduler might improve the model training efficiency without requiring huge amounts of labeled data.
For another example, practitioners in industry often need to improve prediction performance by training many related tasks.
But the results are not always positive and practitioners have a hard time figuring out why.
Our proposed metric can provide guidance for selecting which tasks should be trained together in a multi-task model.

%Our algorithmic consequences of our theory have the potential to impact downstream applications of multi-task learning.
%For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
%Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult to acquire large amounts of labeled data.
%For such settings, training multi-task models can be very challenging.
%Our insight on using single-task learning results to help understand multi-task learning can be valuable for helping practitioners understand their results.
